Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-23 cbm-rbd-paper.tex
procedure figure

@@

The first failure history was underlying the illustrations
in Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
Here, we observe
$P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$ and $H = 8$,
and in following the system until $\tnow = 8$,
all other failure times are right-censored.
Failures observed for type $C$ are thus considerably later than expected,
while for type $P$, the two observed failures are close to the assumed MTTF. 
Both failure at time $8$ for $H$ and non-failure by time $8$ for $M$ are nothing unusual.
In total, due to the late type $C$ failures, prior assumptions are somewhat pessimistic.
This is reflected in Figure~\ref{fig:tauhist1fig2},
where $\tausnow$ first decreases but then tends to increase
during failure-free periods, adjusting prior expectations since none of the type $C$ components fail.

>>>>

\begin{figure}
\centering
\begin{tikzpicture}
[node distance=10mm,
 font=\footnotesize,
 box/.style={draw, rectangle, thick, minimum height=6mm, minimum width=26mm, rounded corners=2mm},
 pfeil/.style={-latex', very thick}]
\node (startup) [box]                       {\parbox{20ex}{\centering system start-up\\ (all comp.\ new)}};
\node (sysfail) [box, right=of startup]     {system failed?};
\node (tauchck) [box, below=6mm of sysfail] {$\tausnow < \tthresh$?};
\node (gotonxt) [box, below=6mm of tauchck] {\parbox{15ex}{\centering continue to\\ next $\tnow$}};
\draw [thick, dashed, rounded corners=2mm] ($(gotonxt.south east) + (2mm,-1mm)$) rectangle ($(sysfail.north west) + (-5mm,1mm)$) node[above left=0mm and -14mm] {each $\tnow$};
\node [above left=0mm and -8mm of startup] {$t=0$};
\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ cost $c_u$}};
\node (prevent) [box, right=of tauchck, minimum width=18mm] {\parbox{14ex}{\centering preventive\\ maintenance\\ cost $c_p$}};
\node (update) [box, below right=10mm and -4mm of prevent, minimum width=10mm] {\parbox{12ex}{\centering update parameters}};
\draw[pfeil] (startup) -- (sysfail);
\draw[pfeil] (sysfail) -- (tauchck) node[midway, right] {no};
\draw[pfeil] (tauchck) -- (gotonxt) node[midway, right] {no};
\draw[very thick] (gotonxt.west) -- ++(-3mm,0mm) -- ($(sysfail.west) + (-3mm,0mm)$);
\draw[pfeil] (sysfail) -- (correct) node[midway, above] {yes};
\draw[pfeil] (tauchck) -- (prevent) node[midway, above] {yes};
\draw[pfeil] (correct) -| (update);
\draw[pfeil] (prevent) -| (update);
\draw[pfeil] (update) -| (startup) node[midway, below right] {start new cycle};
\end{tikzpicture}
\caption{***operational procedure}
\label{fig:procedure}
\end{figure}

@@

In the first failure history, we observe
$P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$ and $H = 8$,
and in following the system until $\tnow = 8$,
all other failure times are right-censored.
This is failure history used for Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
Failures observed for type $C$ are thus considerably later than expected,
while for type $P$, the two observed failures are close to the assumed MTTF. 
Both failure at time $8$ for $H$ and non-failure by time $8$ for $M$ are nothing unusual.
In total, due to the late type $C$ failures, prior assumptions are somewhat pessimistic.
This is reflected in Figure~\ref{fig:tauhist1fig2},
where $\tausnow$ first decreases but then tends to increase
during failure-free periods, adjusting prior expectations since none of the type $C$ components fail.
